\documentclass{resumestyle}

\begin{document}

% ----------HEADING----------
\resumeHeader
  {George Bolmida}
  
\contactInfo  
  {\href{tel:+19373219502}{(937) 321-9502} \textbullet \ \href{mailto:gbolmida@georgebolmida.com}{gbolmida@georgebolmida.com} \textbullet \ \href{https://georgebolmida.com}{georgebolmida.com}}

% -----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cincinnati}{Cincinnati, OH}
      {Bachelor of Science in Cybersecurity}{April 2023}
    \resumeSubheading
      {Sinclair Community College}{Dayton, OH}
      {Associate of Science in Secure Systems Administration}{May 2021}
  \resumeSubHeadingListEnd

% --------SKILLS--------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Languages/Systems:} Golang, Kubernetes, Python, JavaScript/TypeScript, AWS, Google Cloud, Terraform,\\ CI/CD, Prometheus/Grafana, SQL}
    \resumeSubItem{\textbf{Libraries/Frameworks:} Go Fiber, NextJS, Flask, Cobra CLI, LangChain, Prisma, Gorm}
    \resumeSubItem{\textbf{Communication:} Excelled at articulating technical strategies and requirements with team members and stakeholders to ensure alignment and project success.}
    \resumeSubItem{\textbf{Problem Solving:} Adept at quickly innovating solutions to complex technical problems, ensuring they align with project requirements.}
    \resumeSubItem{\textbf{Versatility:} Quickly adapted to changing project needs and technologies, maintaining high productivity under pressure.}
  \resumeSubHeadingListEnd

% --------WORK EXPERIENCE--------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Datacrate.io}{Cincinnati, OH}
      {Co-Founder \& CTO}{Sep 2023 - January 2024}
      \resumeItemListStart
        \resumeItem{Collaboratively shaped the company's technical strategy, adapting to changing needs and contributing to key decision-making processes.}
        \resumeItem{Spearheaded the development of multiple prototypes with rapidly changing requirements.}
        \resumeItem{Engaged directly with users and technical community members to gather feedback, integrating insights into product development for targeted improvements.}
        \resumeItem{Developed and refined pitch presentations for potential investors, focusing on the company’s value proposition and market potential.}
        \resumeItem{Took initiative in applying for funding from venture capitalists.}
      \resumeItemListEnd
    \resumeSubheading
      {Tangram Flex}{Dayton, OH (Remote)}
      {DevOps Engineer}{Jan 2022 - Sep 2023}
      \resumeItemListStart
        \resumeItem{Managed a critical GitLab instance on Kubernetes for an external customer, integral to a \$95 million contract, supporting 100+ developers.}
        \resumeItem{Led deployment, configuration, and troubleshooting of production applications using Terraform, Kubernetes, and AWS, ensuring high system reliability.}
        \resumeItem{Enhanced GitLab CI/CD pipelines, significantly streamlining testing and deployment processes for both internal and external applications.}
        \resumeItem{Contributed to the development of new functionalities for the product's Helm chart, improving automation and operational efficiency.}
      \resumeItemListEnd
    \resumeSubheading
      {Cyber@UC}{Cincinnati, OH}
      {Head of Lab}{Jan 2022 - Dec 2022}
      \resumeItemListStart
        \resumeItem{Led in planning and implementation of the architecture of both internal and cloud-based infrastructure for the club, utilizing on-premises Kubernetes clusters and Google Cloud.}
        \resumeItem{Streamlined software deployment processes by implementing Terraform and Helm, achieving a highly organized and unified system setup.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% --------PROJECTS--------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Raspberry Pi Kubernetes Cluster:} Built a 6-node Kubernetes cluster on Raspberry Pis. This setup included Gitea and Drone CI implementations, plus Prometheus/Grafana for monitoring, all managed via ArgoCD with GitOps.}
    \resumeSubItem{\textbf{NixOS GitOps Server:} Collaborated on a cloud-native web app with React and Golang for remote device management and Linux workstation customization via UI or GitOps with GitHub.}
    \resumeSubItem{\textbf{This Resume:} Fully automated the process of building and publishing this resume with LaTeX, Github Actions, and S3.}
  \resumeSubHeadingListEnd

% --------CERTIFICATIONS--------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{AWS Solutions Architect - Associate:} Amazon Web Services - \textit{January 2023}}
    \resumeSubItem{\textbf{Certified Kubernetes Administrator:} The Linux Foundation - \textit{December 2021}}
    \resumeSubItem{\textbf{CompTIA Security+:} CompTIA - \textit{July 2021}}
  \resumeSubHeadingListEnd

\end{document}
